Relating games of Menger, countable fan tightness, and selective separability

### 2018-03-06 articles/relating-games-menger-cft-ss/article.tex
add improvements and further results suggested by referee

\begin{proposition}
  Any witness for \(\Omega M\) (resp.
  \(\Omega M^+,\Omega M^{\plusMark}\))
  may be improved so that any final sequence of the chosen
  finite subcollections is an \(\omega\)-cover.
\end{proposition}

\begin{proof}
  Consider any sequence \(\<\mc U_0,\mc U_1,\dots\>\) of \(\omega\)-covers.
  For each \(n<\omega\), let
  \(\<\mc F_n^n,\mc F_{n+1}^n,\dots\>\) witness \(\Omega M\) for the final
  sequence \(\<\mc U_n,\mc U_{n+1},\dots\>\),
  and let \(\mc F_n=\bigcup_{i\leq n}\mc F_n^i\); it follows that
  \(\<\mc F_0,\mc F_1,\dots\>\) satisfies the proposition.

  For \(\Omega M^+\), the winning strategy \(\sigma\) may be improved to
  \(\tau\) where
  \(
    \tau(\<\mc U_0,\dots,\mc U_n\>)
      =
    \bigcup_{i\leq n}\sigma(\<\mc U_i,\dots,\mc U_n\>)
  \). For \(\Omega M^{\plusMark}\), the winning Markov strategy \(\sigma\) may
  be improved to \(\tau\) where
  \(
    \tau(\mc U,n)
      =
    \bigcup_{i\leq n}\sigma(\mc U,i)
  \). Both improved strategies are easily seen to satisfy the proposition.
\end{proof}

@@

@@

\begin{proof}
  In Lemmas \ref{mengerFanLemma1} and \ref{mengerFanLemma2},
  \(|\tau(t)|=|\sigma(t)|\). Therefore they may be extended to
  the strong cases requiring \(|\tau(t)|=|\sigma(t)|=1\),
  which yields our result.
\end{proof}

@@

\begin{lemma}
  Let \(\mc A\) be a family of sets where
  \(|\bigcup\mc A|\leq\omega\)
  and let \(\mc B\) be a family of sets closed under supersets. Then
  \(\plII\win\schStrongSelGame{\mc A}{\mc B}\) if and only if
  \(\plII\markwin\schStrongSelGame{\mc A}{\mc B}\).
\end{lemma}

\begin{proof}
  In the proof of Lemma \ref{mainLemma}, \(|\tau(t)|=|\sigma(t)|\).
\end{proof}

@@

\section{Acknowledgements}
The author would like to thank Ziqin Feng and Gary Gruenhage
for their helpful comments on the topic of \(C_p(\onePtLind{\omega_1})\).

>>>>

\begin{proposition}\label{cofinalSequence}
  Let \(\mc A\), \(\mc B\) be families of sets such that
  \(B\in\mc B\) and \(B\subseteq B'\subseteq\bigcup\mc A\)
  implies \(B'\in\mc B\).
  Then any witness for \(\schSelProp{\mc A}{\mc B}\)
  may be improved so that any final sequence of the sets chosen by \(\plII\)
  belongs to \(\mc B\).

  Furthermore, any witness for
  \(\plII\win\schSelGame{\mc A}{\mc B}\) or
  \(\plII\markwin\schSelGame{\mc A}{\mc B}\)
  may be improved so that any subsequence of the sets chosen by \(\plII\)
  belongs to \(\mc B\).
\end{proposition}

\begin{proof}
  Let \(A_n\in\mc A\) for \(n<\omega\), and suppose
  \(\<B_{n,n},B_{n+1,n},\dots\>\) witnesses \(\schSelProp{\mc A}{\mc B}\)
  for \(\<A_n,A_{n+1},\dots\>\).
  Let \(B_n=\bigcup_{i\leq n}B_{n,i}\); it follows that
  \(\<B_0,B_1,\dots\>\) satisfies the proposition.

  Let \(s\preceq t\) indicate that \(s\) is a subsequence
  of \(t\). Then for \(\plII\win\schSelGame{\mc A}{\mc B}\),
  the winning strategy \(\sigma\) may be improved to
  \(\tau\) where
  \(
    \tau(t\concat\<A\>)
      =
    \bigcup_{s\preceq t}\sigma(s\concat\<A\>)
  \).
  For \(\plII\markwin\schSelGame{\mc A}{\mc B}\),
  the winning Markov strategy \(\sigma\) may
  be improved to \(\tau\) where
  \(
    \tau(A,n)
      =
    \bigcup_{i\leq n}\sigma(A,i)
  \). Both improved strategies are easily seen to satisfy the proposition.
\end{proof}

It's worth noting that Gruenhage applied a similar technique used above
for strategies in \(\schSelGame{\mc A}{\mc B}\) to obtain strengthened
strategies in his game played with open neighborhoods and points in
\cite{MR0413049}.

@@

We conclude this section by covering a related result observed by the
anonymous referee in their initial review of this manuscript.

\begin{theorem}
  A topological space is \(M^+\) if and only if it is \(\Omega M^+\).
\end{theorem}

\begin{proof}
  Assume \(X\) is \(M^+\). In \cite[Proposition 5.1]{MR3383283} it is shown
  that that \(X^m\) must be \(M^+\) for all powers \(m<\omega\), so we shall
  proceed in the spirit of Proposition \ref{altCompactCharacterization}
  and its following lemma. Given an \(\omega\)-cover \(\mc U\),
  it follows that \((\mc U)^m=\{U^m:U\in\mc U\}\) is an open cover of
  \(X^m\). Given a finite subset \(\mc F\in[(\mc U)^m]^{<\omega}\),
  let \(\pi_m\mc F=\{U:U^m\in\mc F\}\in[\mc U]^{<\omega}\).

  Let \(\sigma_m\) witness \(M^+\) for \(X^m\), and define
  the following strategy for \(\plII\) in \(\schSelGame{\Omega}{\Omega}\):
  \[
    \tau(\<\mc U_0,\dots,\mc U_n\>)
      =
    \bigcup_{m\leq n}
    \pi_m\sigma_m(\<(\mc U_m)^m,\dots,(\mc U_n)^m\>)
  .\]
  Since
  \[
    \bigcup_{m\leq n<\omega}
    \sigma_m(\<(\mc U_m)^m,\dots,(\mc U_n)^m\>)
  \]
  is an open cover of \(X^m\) for \(m<\omega\), it follows that
  \[
    \bigcup_{n<\omega}
    \tau(\<\mc U_0,\dots,\mc U_n\>)
      \supseteq
    \bigcup_{m\leq n<\omega}
    \pi_m\sigma_m(\<(\mc U_m)^m,\dots,(\mc U_n)^m\>)
  \]
  covers all finite sets of size \(m<\omega\), that is,
  \(
    \bigcup_{n<\omega}
    \tau(\<\mc U_0,\dots,\mc U_n\>)
  \)
  is an \(\omega\)-cover, making \(\tau\) a winning strategy.
\end{proof}

@@

\begin{proof}
  In the proof of Lemmas \ref{mengerFanLemma1} and \ref{mengerFanLemma2},
  if the strategy \(\sigma\) produces singletons, so does the strategy
  \(\tau\).
\end{proof}

@@

\begin{lemma}
  Let \(\mc A\) be a family of sets where
  \(|\bigcup\mc A|\leq\omega\)
  and let \(\mc B\) be a family of sets such that
  \(B\in\mc B\) and \(B\subseteq B'\subseteq\bigcup\mc A\)
  implies \(B'\in\mc B\). Then
  \(\plII\win\schStrongSelGame{\mc A}{\mc B}\) if and only if
  \(\plII\markwin\schStrongSelGame{\mc A}{\mc B}\).
\end{lemma}

\begin{proof}
  In the proof of Lemma \ref{mainLemma},
  if the perfect information strategy \(\sigma\) always
  produces singletons, so does the Markov strategy \(\tau\).
\end{proof}

@@

\section{Acknowledgements}
The author would like to thank Ziqin Feng and Gary Gruenhage
for their helpful comments on the topic of \(C_p(\onePtLind{\omega_1})\).
The author also thanks the anonymous referree who pointed out
the game strategies in Proposition \ref{cofinalSequence} could handle all
subsequences rather than only final sequences, in addition to the
observation given as the final result of the third section.
